Estimating the replicability of psychology experiments after an initial failure to replicate

### 2024-04-12 manuscript/manuscript.Rmd
fix figure by adding a period

level_order = c("Yeshurun & Levy 2003",
                "Ngo et al. 2019", 
                 "Krauss & Wang 2003",
                 "Jara-Ettinger et al 2022")
smd_scale_big <- ggplot(for_plotting_d |> inner_join(big) |> 
                          mutate(name_pretty=factor(name_pretty, levels=level_order)), aes(x=name_pretty,y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
 coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
    scale_shape_manual(values=shape)+
  theme(legend.position = "none", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="", )

>>>>

level_order = c("Yeshurun & Levy 2003",
                "Ngo et al. 2019", 
                 "Krauss & Wang 2003",
                 "Jara-Ettinger et al. 2022")
smd_scale_big <- ggplot(for_plotting_d |> inner_join(big) |> 
                          mutate(name_pretty=factor(name_pretty, levels=level_order)), aes(x=name_pretty,y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
 coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
    scale_shape_manual(values=shape)+
  theme(legend.position = "none", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="", )
